---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# summarize_stats package

<!-- badges: start -->

<!-- badges: end -->

The **summarize_stats** package contains the function *summarize_stats* that generates the mean, median, and the range values of a numeric variable across a categorical variable. This facilitates the comparison of these summary statistics across different groups within a categorical variable of interest, allowing for further downstream analyses.

## Installation

You can install the latest version of summarize_stats from [GitHub](https://github.com/) with:

``` r
`devtools::install_github('stat545ubc-2025/summarize_stats')`
```

## Examples of use cases

Example using the steam_games dataset from the *datateachr* package. Investigate the summary statistics of **Steam game prices** (numerical variable) across **purchase types** (factor variable).   

```{r example 1}
library(summarizestats)
library(datateachr) #contains the steam_games dataset
summarize_stats(df = datateachr::steam_games, numcol = original_price, categcol = types, NAs = TRUE)
```

Example using the penguins dataset from the *palmerpenguins* package. Investigate the summary statistics of **bill length** (numerical variable) based on **penguin sex** (factor variable). 

```{r example 2}
library(palmerpenguins) #contains the penguins dataset
summarize_stats(df = penguins, numcol = bill_depth_mm, categcol = sex, NAs = TRUE)
```

## Getting Help

If you have any issues installing/running the package, or if you have any suggestions for improvements, feel free to leave an issue!
